Empirical Check of Machine Homogeneity on Timing Protocol

### 2018-09-27 pt_characterization/machine_cons_check/post_exp.tex
Rick's concerns being handled

For the same task length, or INC16, 
I examined in each of the four runs a few iterations at which more than three daemons (except INC and proc monitor processes) that had positive PT were captured.  
From Table~\ref{fig:daemon}, I suspect that PT distribution seems most likely to be affected by two facts: {\it how longer the same daemon ran than usual}, and {\it how many different daemon processes appeared and how long it ran}.

\begin{table}[htp!]
\centering
{
 \begin{tabular}{|p{1.5cm}|p{2cm}|p{12.5cm}|} \hline
Machine Name & Iteration \# & Process Name (id, PT(msec))\\ \hline
{\tt sodb8}  & 174 & {\tt java} ({\tt 2349}, 15), {\tt java} ({\tt 2335}, 2),  {\tt md127\_raid1} ({\tt 457}, 1), {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
 					& 278 & {\tt java} ({\tt 2877}, 16), {\tt java} ({\tt 2335}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
			  &  486 & {\tt java} ({\tt 3190}, 21), {\tt java} ({\tt 2335}, 2),  {\tt md127\_raid1} ({\tt 457}, 1), {\tt kslowd000} ({\tt 166}, 1)\\ \cline{2-3}
				  &  526 & {\tt md127\_raid1} ({\tt 457}, 1), {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1), {\tt jbd2/md127-8} ({\tt 470}, 1)\\ \cline{2-3}
				  &  555 & {\tt java} ({\tt 3815}, 8), {\tt java} ({\tt 2335}, 2), {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1)\\ \hline
{\tt sodb9}  & 105 & {\tt java} ({\tt 6634}, 16), {\tt java} ({\tt 6621}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
				  & 175 & {\tt java} ({\tt 6942}, 7), {\tt java} ({\tt 6621}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
				  & 245 & {\tt java} ({\tt 7259}, 6), {\tt java} ({\tt 6621}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
				  & 280 & {\tt java} ({\tt 7365}, 3), {\tt java} ({\tt 6621}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
				  & 350 & {\tt java} ({\tt 7577}, 3), {\tt java} ({\tt 6621}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
				  & 420 & {\tt java} ({\tt 7683}, 3), {\tt java} ({\tt 6621}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
				  & 490 & {\tt java} ({\tt 7894}, 4), {\tt java} ({\tt 6621}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \hline
{\tt sodb10}  & 105 & {\tt java} ({\tt 28394}, 14), {\tt java} ({\tt 28381}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
					 & 314 & {\tt java} ({\tt 28702}, 18), {\tt java} ({\tt 28381}, 2),  {\tt md127\_raid1} ({\tt 455}, 1),  {\tt kslowd001} ({\tt 167}, 1) \\ \hline
 {\tt sodb12}  & 280 &  {\tt kslowd001} ({\tt 167}, 154),  {\tt kslowd000} ({\tt 166}, 150), {\tt java} ({\tt 14820}, 37), {\tt java} ({\tt 14807}, 2) \\ \cline{2-3}
	& 311 &  {\tt kslowd000} ({\tt 166}, 154),  {\tt kslowd001} ({\tt 167}, 153), {\tt java} ({\tt 14807}, 2), {\tt java} ({\tt 15653}, 1), {\tt khugepaged} ({\tt 30}, 1)\\ \cline{2-3}		& 373 &  {\tt kslowd000} ({\tt 166}, 154),  {\tt kslowd001} ({\tt 167}, 152), {\tt java} ({\tt 14807}, 2), {\tt java} ({\tt 15747}, 2)\\ \cline{2-3}
& 435 &  {\tt kslowd000} ({\tt 166}, 154),  {\tt kslowd001} ({\tt 167}, 153), {\tt java} ({\tt 15934}, 6), {\tt java} ({\tt 14807}, 2)\\ \cline{2-3}
& 466 &  {\tt kslowd000} ({\tt 166}, 152), {\tt java} ({\tt 16121}, 6), {\tt java} ({\tt 14807}, 2), {\tt kblockd/0} ({\tt 16}, 1)\\ \cline{2-3}
 \hline
 \end{tabular}
  }
 \caption{Some daemon processes captured across different machines~\label{fig:daemon}}
\end{table}

>>>>

For the same task length, or INC16, 
I examined in each of the four runs a few iterations at which more than three daemons (except INC and proc monitor processes) that had positive PT were captured.  
From Table~\ref{tab:daemon}, I suspect that PT distribution seems most likely to be affected by two facts: {\it how longer the same daemon ran than usual}, and {\it how many different daemon processes appeared and how long it ran}.

\begin{table}[htp!]
\centering
{
 \begin{tabular}{|p{1.5cm}|p{2cm}|p{12.5cm}|} \hline
Machine Name & Iteration \# & Process Name (id, PT(msec))\\ \hline
{\tt sodb8}  & 174 & {\tt java} ({\tt 2349}, 15), {\tt java} ({\tt 2335}, 2),  {\tt md127\_raid1} ({\tt 457}, 1), {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
 					& 278 & {\tt java} ({\tt 2877}, 16), {\tt java} ({\tt 2335}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
			  &  486 & {\tt java} ({\tt 3190}, 21), {\tt java} ({\tt 2335}, 2),  {\tt md127\_raid1} ({\tt 457}, 1), {\tt kslowd000} ({\tt 166}, 1)\\ \cline{2-3}
				  &  526 & {\tt md127\_raid1} ({\tt 457}, 1), {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1), {\tt jbd2/md127-8} ({\tt 470}, 1)\\ \cline{2-3}
				  &  555 & {\tt java} ({\tt 3815}, 8), {\tt java} ({\tt 2335}, 2), {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1)\\ \hline
{\tt sodb9}  & 105 & {\tt java} ({\tt 6634}, 16), {\tt java} ({\tt 6621}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
				  & 175 & {\tt java} ({\tt 6942}, 7), {\tt java} ({\tt 6621}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
				  & 245 & {\tt java} ({\tt 7259}, 6), {\tt java} ({\tt 6621}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
				  & 280 & {\tt java} ({\tt 7365}, 3), {\tt java} ({\tt 6621}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
				  & 350 & {\tt java} ({\tt 7577}, 3), {\tt java} ({\tt 6621}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
				  & 420 & {\tt java} ({\tt 7683}, 3), {\tt java} ({\tt 6621}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
				  & 490 & {\tt java} ({\tt 7894}, 4), {\tt java} ({\tt 6621}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \hline
{\tt sodb10}  & 105 & {\tt java} ({\tt 28394}, 14), {\tt java} ({\tt 28381}, 2),  {\tt kslowd000} ({\tt 166}, 1), {\tt kslowd001} ({\tt 167}, 1) \\ \cline{2-3}
					 & 314 & {\tt java} ({\tt 28702}, 18), {\tt java} ({\tt 28381}, 2),  {\tt md127\_raid1} ({\tt 455}, 1),  {\tt kslowd001} ({\tt 167}, 1) \\ \hline
 {\tt sodb12}  & 280 &  {\tt kslowd001} ({\tt 167}, 154),  {\tt kslowd000} ({\tt 166}, 150), {\tt java} ({\tt 14820}, 37), {\tt java} ({\tt 14807}, 2) \\ \cline{2-3}
	& 311 &  {\tt kslowd000} ({\tt 166}, 154),  {\tt kslowd001} ({\tt 167}, 153), {\tt java} ({\tt 14807}, 2), {\tt java} ({\tt 15653}, 1), {\tt khugepaged} ({\tt 30}, 1)\\ \cline{2-3}		& 373 &  {\tt kslowd000} ({\tt 166}, 154),  {\tt kslowd001} ({\tt 167}, 152), {\tt java} ({\tt 14807}, 2), {\tt java} ({\tt 15747}, 2)\\ \cline{2-3}
& 435 &  {\tt kslowd000} ({\tt 166}, 154),  {\tt kslowd001} ({\tt 167}, 153), {\tt java} ({\tt 15934}, 6), {\tt java} ({\tt 14807}, 2)\\ \cline{2-3}
& 466 &  {\tt kslowd000} ({\tt 166}, 152), {\tt java} ({\tt 16121}, 6), {\tt java} ({\tt 14807}, 2), {\tt kblockd/0} ({\tt 16}, 1)\\ \cline{2-3}
 \hline
 \end{tabular}
  }
 \caption{Some daemon processes captured across different machines~\label{tab:daemon}}
\end{table}

Similarly, we looked at the data from INC128 on {\tt sodb12}.

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb12}  (plugged into the {\em upper right} power strip) &  INC128 & Runs of 1,000 samples & 2017-02-09$\sim$2017-02-10\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of the INC128 data\label{tab:exp_notes5}}
\end{table}

Table~\ref{tab:daemon2} shows a list of daemon processes observed at some iterations for which more than three daemons revealed positive PT while the INC128 program was run.
\begin{table}[htp!]
\centering
{
 \begin{tabular}{|p{1.5cm}|p{2cm}|p{12.5cm}|} \hline
Machine Name & Iteration \# & Process Name (id, PT(msec))\\ \hline
 {\tt sodb12}  & 33 & {\tt flush-9:0} ({\tt 25187}, 1), {\tt java} ({\tt 304}, 1), {\tt java} ({\tt 32627}, 3), {\tt md0\_raid1} ({\tt 484}, 1) \\ \cline{2-3}
					  & 138  & {\tt flush-9:0} ({\tt 25187}, 1), {\tt java} ({\tt 734}, 1), {\tt java} ({\tt 32627}, 3), {\tt md0\_raid1} ({\tt 484}, 1)  \\ \cline{2-3}
					  & 181 & {\tt flush-9:0} ({\tt 25187}, 1), {\tt java} ({\tt 908}, 1), {\tt java} ({\tt 32627}, 3), {\tt jbd2/md0-8} ({\tt 497}, 1) \\ \cline{2-3}
				     & 228 &  {\tt flush-9:0} ({\tt 25187}, 1), {\tt java} ({\tt 1099}, 1), {\tt java} ({\tt 32627}, 3), {\tt md0\_raid1} ({\tt 484}, 1)\\ \cline{2-3}
 \hline
 \end{tabular}
  }
 \caption{Some daemon processes captured at some iterations of INC128~\label{tab:daemon2}}
\end{table}

Table~\ref{tab:exp_notes6} gives a background description of what environment 
was set for running the MATR8K program.

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb12} (plugged into {\em the upper right} power strip) & MATR8K& Runs of 300 samples & 2018-03-02 $\sim$2018-03-12 \\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of the MATR8K data\label{tab:exp_notes6}}
\end{table}

Table~\ref{tab:daemon3} shows a list of daemon processes 
observed at some iterations for which a number of daemons revealed positive PT while the MATR8K program was run.
\begin{table}[htp!]
\centering
{ %{\tt bash} ({\tt 17403}, 1), {\tt bash} ({\tt 17400}, 7),  
 \begin{tabular}{|p{1.5cm}|p{2cm}|p{12.5cm}|} \hline
Machine Name & Iteration \# & Process Name (id, PT(msec))\\ \hline
 {\tt sodb12}  & 
 36 & ({\tt MATR8K} ({\tt 17244}, 2183274),{\tt proc\_monitor} ({\tt 14166}, 200)), 
 {\tt kslowd001} ({\tt 167}, 16959),  {\tt kslowd000} ({\tt 166}, 16707), 
 {\tt md0\_raid1 } ({\tt 482}, 19),  {\tt sshd} ({\tt 17398}, 18), {\tt bash}  ({\tt 17400}, 7),  
 {\tt flush-9:0} ({\tt 718}, 3), {\tt java} ({\tt 17234}, 2), {\tt kblockd/0} ({\tt 16}, 2), 
 {\tt grep} ({\tt 17406}, 1), {\tt sshd} ({\tt 17399}, 1), 
 {\tt events/0} ({\tt 7}, 1), {\tt bash} ({\tt 17403}, 1))\\ \cline{2-3} 
&  119 & ({\tt MATR8K} ({\tt 17244}, 2183217),{\tt proc\_monitor} ({\tt 14166}, 204))
 {\tt kslowd001} ({\tt 167}, 16784),  {\tt kslowd000} ({\tt 166}, 16839), 
 {\tt md0\_raid1 } ({\tt 482}, 16),  {\tt  jbd2/md0-8} ({\tt 495}, 13), 
 {\tt sshd} ({\tt 17773}, 7), {\tt sshd} ({\tt 17771}, 7), 
 {\tt kblockd/0} ({\tt 16}, 4),  {\tt events/0} ({\tt 7}, 3), 
 {\tt flush-9:0} ({\tt 718}, 3), {\tt java} ({\tt 17234}, 2), 
 {\tt sshd} ({\tt 17772}, 2),  {\tt sshd} ({\tt 2148}, 1), 
 {\tt java} ({\tt 17768}, 2), {\tt sshd} ({\tt 17774}, 1)\\ \cline{2-3}
 \hline
 \end{tabular}
  }
 \caption{Some daemon processes captured at some iterations of MATR8K~\label{tab:daemon3}}
\end{table}
